Online Social Cohesion Reflects Real-World Group Action in Syria during the Arab Spring

### 2020-05-25 manuscript.Rmd
Tweaks to authorship info

author: 
  - name          : "Megan Chiovaro"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "406 Babbidge Road, Unit 1020, Storrs, CT 06269"
    email         : "megan.chiovaro@uconn.edu"
  - name          : "Alexandra Paxton"
    affiliation   : "1,2,*"
  - name          : "Lead C. Windsor"
    affiliation   : "3,*"

affiliation:
  - id            : "1"
    institution   : "Center for the Ecological Study of Perception and Action"
  - id            : "2"
    institution   : "University of Connecticut"
  - id            : "3"
    institution   : "University of Memphis"
  - id            : "*"
    institution   : "Equal author contributions"

>>>>

author: 
  - name          : "Megan Chiovaro"
    affiliation   : "1, 2"
    corresponding : yes    # Define only one corresponding author
    address       : "406 Babbidge Road, Unit 1020, Storrs, CT 06269"
    email         : "megan.chiovaro@uconn.edu"
  - name          : "Alexandra Paxton"
    affiliation   : "1,2,*"
  - name          : "Leah C. Windsor"
    affiliation   : "3,*"

affiliation:
  - id            : "1"
    institution   : "Center for the Ecological Study of Perception and Action, University of Connecticut"
  - id            : "2"
    institution   : "Department of Psychological Sciences, University of Connecticut"
  - id            : "3"
    institution   : "University of Memphis"
  - id            : "*"
    institution   : "Equal author contributions"
